Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-24 background.tex
2015.05.17 (Vassilis) Enabled ancoring for the motivation subsection of the background section. Enabled ancoring for histogram figures (efficiency, overhead, scalability). Elaborated on connection sentences for both (unstructured and structured) discussion sections. Some minor re-wording and image re-scaling for better typesetting.
2015.05.18 (Alex) Gone through spelling correction. Added minimal biography text for authors. Some more re-wording on the connection sentences in the discussion section. Moving table and plots to improve overall typesetting in the structured section.

\emph{Decentralized structured schemes} were introduced as an answer to the above
problems of decentralized unstructured \p--approaches
(Figure~\ref{figure:p2p-archs:structured}).
Here, the main objective was to offer 
a self-organizing infrastructure for large-scale \p\ applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
To achieve that, they implement a \emph{Distributed Hash Table (DHT)} that maps
objects to nodes through a deterministic mechanism. \emph{DHT}s provide a
guaranteed bound on the number of overlay routing hops that have to be
``traveled'' to locate a resource, even in the case when only a \emph{single}
copy exists whithin the system. This requires
$O$($log(n)$) hops, compared to the unstructured networks that require
$O(n)$ to reliably locate any object. Unfortunately this efficiency does not
come without cost. Structured overlays can only support exact-match queries 
(i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. 
This means that unstructured overlays can support more versatile 
resource location queries such as keyword and partial matching searches. 
Several popular file-sharing \p\ applications have been based on \emph{DHT}s
including {\sl Overnet}/{\sl eDonkey}~\cite{overnet}, 
{\sl Kademlia}/{\sl Kad Network}~\cite{maymounkov_kademlia_2002},  and 
some flavors of {\sl BitTorrent}~\cite{c_bittorrent_2003}.  
Moreover, \emph{DHT}s sparked
a flurry of research for many, diverse, applications ranging
from distributed search engines to event-notification and cloud-based
platforms~\cite{kbc_oceanstore_2000,rkcd_scribe_2001,mgpj_cloudsnap_2011}.

@@

Early overlay protocol implementations did not pay much attention to map
optimally to the underlying network topology. {\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach the node(s) having the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superflous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology--unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it completely ignores
how the actual packets are switched at the underlying infrastructure along
the overlay path. 
In particular, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. 
Moreover, a link in the physical network often lies
on several overlay paths inadvertently increasing the traffic on that
link; this is known as the link's \emph{stress}~\cite{CRSZ2002}. 
There is also the stochastic phenomenon during which peers 
depart and others arrive in the network, known 
as \emph{churn}~\cite{stutzbach_churn_2006}.
Even when an approach offers the best possible location
when a node joins in, the churn is set to  
continuously undermine the effort to maintain the best possible position
of the  peer in the network.

@@

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if the are proven to
effectivelly support hundreds, tenths of thousands or millions of nodes,
respectively.
%%%VM Reworked definition.
%%

>>>>

\emph{Decentralized structured schemes} were introduced as an answer to the above
problems of decentralized unstructured \p--approaches
(Figure~\ref{figure:p2p-archs:structured}).
Here, the main objective was to offer 
a self-organizing infrastructure for large-scale \p\ applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
To achieve that, they implement a \emph{Distributed Hash Table (DHT)} that maps
objects to nodes through a deterministic mechanism. \emph{DHT}s provide a
guaranteed bound on the number of overlay routing hops that have to be
``traveled'' to locate a resource, even in the case when only a \emph{single}
copy exists within the system. This requires
$O$($log(n)$) hops, compared to the unstructured networks that require
$O(n)$ to reliably locate any object. Unfortunately this efficiency does not
come without cost. Structured overlays can only support exact-match queries 
(i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. 
This means that unstructured overlays can support more versatile 
resource location queries such as keyword and partial matching searches. 
Several popular file-sharing \p\ applications have been based on \emph{DHT}s
including {\sl Overnet}/{\sl eDonkey}~\cite{overnet}, 
{\sl Kademlia}/{\sl Kad Network}~\cite{maymounkov_kademlia_2002},  and 
some flavors of {\sl BitTorrent}~\cite{c_bittorrent_2003}.  
Moreover, \emph{DHT}s sparked
a flurry of research for many, diverse, applications ranging
from distributed search engines to event-notification and cloud-based
platforms~\cite{kbc_oceanstore_2000,rkcd_scribe_2001,mgpj_cloudsnap_2011}.

@@

Early overlay protocol implementations did not pay much attention to map
optimally to the underlying network topology. {\sl Gnutella}, for example, is
considered far from scalable~\cite{ritter_gnucantscale_2001} for every peer
chooses its neighbors without any knowledge of the underlying
network, resulting in mismatches. 
Queries are flooded over multiple paths in an effort 
to reach the node(s) having the sought content. 
In addition, 
pairs of nodes may simultaneously forward the same query to each other
in a superfluous mode of operation in 
this opportunistic and without coordination environment.
%%
\cite{matei_mapgnutella_2002} showed that, even when $95$\% of any two nodes 
are less than $7$ hops away from each other, 
a \emph{flooding-based} {\sl Gnutella}-like algorithm 
can generate $330$TB/month traffic in a $50,000$ node network. 
A topology mismatch can thus have a serious effect 
on Internet's routing performance.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
\label{background:motivation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology--unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it completely ignores
how the actual packets are switched at the underlying infrastructure along
the overlay path. 
In particular, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. 
Moreover, a link in the physical network often lies
on several overlay paths inadvertently increasing the traffic on that
link; this is known as the link's \emph{stress}~\cite{CRSZ2002}. 
There is also the stochastic phenomenon during which peers 
depart and others arrive in the network, known 
as \emph{churn}~\cite{stutzbach_churn_2006}.
Even when an approach offers the best possible location
when a node joins in, the churn is set to  
continuously undermine the effort to maintain the best possible position
of the  peer in the network.

@@

For the \emph{scalability} criterion, we consider system behavior with respect
to the number of participating peers it can reliably support. We characterize
protocols as being lowly, mediumly or highly scalable if the are proven to
effectively support hundreds, tenths of thousands or millions of nodes,
respectively.
%%%VM Reworked definition.
%%

### 2015-05-24 mard-survey.tex
2015.05.18 (Alex) Gone through spelling correction. Added minimal biography text for authors. Some more re-wording on the connection sentences in the discussion section. Moving table and plots to improve overall typesetting in the structured section.

\begin{IEEEbiography}{Vassilis Moustakas}
Biography text here.
\end{IEEEbiography}

@@

\begin{IEEEbiography}{H\"useyin Akcan}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Mema Roussopoulos}
Biography text here.
\end{IEEEbiography}

\begin{IEEEbiography}{Alex Delis}
Biography text here.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}{Vassilis Moustakas}
% Biography text here.
is a researcher with the University of Athens in Athens, Greece.
\end{IEEEbiography}

@@

\begin{IEEEbiography}{H\"useyin Akcan}
% Biography text here.
is an Associate Professor of Computer Science at Izmir University of Economics in Izmir, Turkey.
\end{IEEEbiography}

\begin{IEEEbiography}{Mema Roussopoulos}
% Biography text here.
is an Associate Professor of Computer Science at the Univ. of Athens in Athens, Greece.
\end{IEEEbiography}

\begin{IEEEbiography}{Alex Delis}
% Biography text here.
is a Professor of Computer Science at the Univ. of Athens in Athens, Greece.
\end{IEEEbiography}
